---
title: "Presentation"
author: "noah"
date: "December 4, 2017"
output: html_document
---

Lots of data exploration inspiration from Michael Griffiths:
https://www.kaggle.com/msjgriffiths/exploratory-analysis/code

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

lib <- function(package_name) {
  if (!require(package_name, character.only = TRUE)) {
    install.packages(package_name, repos = "http://cran.us.r-project.org")
    library(package_name, character.only = TRUE)
  }
}

lib('dplyr')
lib('ggplot2')
theme_set(theme_bw())
lib('tidyverse')
lib('formattable')
lib('plotly')
lib('pander')
panderOptions('table.split.table', Inf)
```

```{r}
# Load data
animes <- read.csv('../data/clean/animes.csv', header = TRUE, stringsAsFactors = FALSE)
genres <- read.csv('../data/clean/genres.csv', header = TRUE, stringsAsFactors = FALSE)
ratings <- read.csv('../data/raw/no_null_ratings.csv', header = TRUE)
```

# Let's look at the top anime by avg rating
```{r}
N <- 10
df <- data.frame(Anime = animes$name, Rating = animes$rating, stringsAsFactors = TRUE) # want names as factors for plotting

df <- df[order(df$Rating, decreasing = TRUE), ]  # sort by ranking
df$Anime <- factor(df$Anime, levels = df$Anime)  # to retain the order in plot
df <- df[1:N,] # cut off the top N

df %>% ggplot(aes(x=Anime, y=Rating)) + 
  geom_bar(stat="identity", width=.5, fill="tomato3") + 
  coord_cartesian(ylim = c(9.0, 10.0)) +
  labs(title="Top Anime Ratings",
       caption="source: MAL dataset") + 
  theme(axis.text.x = element_text(angle=65, vjust=0.6))
```

## Let's explore the distribution of ratings among some different groupings

# First, does type (Movie, TV show,...) matter?
```{r}
animes %>% 
  ggplot(aes(rating, group = type)) +
  labs(title = "Average Anime Ratings by Type") +
  geom_density(aes(fill = type), alpha = .4) +
  xlim(0, 10)
```

# Looks like it does! Let's look more closely at the variation between types
```{r}
animes %>% 
  group_by(type) %>% 
  summarise(
    average.viewers = mean(members),
    sd.viewers = sd(members),
    average.rating = mean(rating, na.rm = T),
    sd.rating = sd(rating, na.rm = T)
  ) %>% 
  formattable()
```


# Explore the genres too!
```{r}
animes_subset_ratings <- animes %>% select("anime_id", "rating")
genres_with_ratings <- inner_join(genres, animes_subset_ratings, by = "anime_id")

g <- genres_with_ratings %>% 
  ggplot(aes(rating, group = genre)) +
  geom_density(aes(fill = genre), alpha = .4)

ggplotly(g)
```

# The Dementia genre is very unpopular. The Harem genre has a very high thin peak, indicating little variance. Maybe they're all basically the same?

# In our dataset, what's the distribution of user ratings?
```{r}
g <- ratings %>% ggplot(aes(x = factor(rating))) +
  geom_bar() + labs(title = "Distribution of ratings")

ggplotly(g)
```

# What about the distribution of users' average rating?
```{r}
g <- ratings %>% 
  group_by(user_id) %>% 
  summarise(m = mean(rating)) %>% 
  ggplot(aes(m)) +
  geom_density() +
  labs(title = "Distribution of average rating over users")

ggplotly(g)
```

# School days is a notoriously controversial anime. Is the variance of users' ratings of this anime higher than it is for most anime?
```{r}
school_days.id <- filter(animes, name == "School Days")$anime_id
school_days.ratings <- filter(ratings, anime_id == school_days.id)
school_days.sd <- sd(school_days.ratings$rating)
print(school_days.sd)

summary(ratings$rating)
ratings.sd <- sd(ratings$rating)
print(ratings.sd)
```

# Yes it is! Let's visualize that
```{r}
#school_days.ratings %>% ggplot(aes(x = bin, y = ..density.., group = source, fill = source)) +
#    geom_bar(alpha = 0.5, position = 'identity')

g <- school_days.ratings %>% ggplot(aes(x = rating))

g + geom_density()
g + geom_bar() # Bar plot

ggplotly(g)

# Create a fake grouping variable, for a boxplot of 1 dim
g + geom_violin(aes(x = factor(0), y = rating), trim = FALSE, adjust = 2) + 
  xlab("") + scale_x_discrete(breaks = NULL)
```
# Yeah, looks like the 
# Let's compute class rankings to find the true Weebs
```{r}
# Weeb score
MAX_SCORE <- 10 # We assume students would give their favorite animes this score
MIN_SCORE <- 1 # We assume students would give their least fav animes this score

students <- c("Adriana", "Beau", "David", "Fanny", "Joe", "Kevin", "Lilly (Ralf)", "Lydia", "Mac", "Michael", "Noah", "Richard", "Roger", "Saad", "Shane", "Stephanie", "Ty", "Xiaotai")
fav_animes <- c("Psycho-Pass", "One Punch Man", "Cowboy Bebop", "", "FLCL", "Death Note", "Last Exile", "JoJo no Kimyou na Bouken (TV)", "Pokemon", "Tonari no Totoro", "Ginga Eiyuu Densetsu", "Afro Samurai", "Yuri!!! on Ice", "Dragon Ball Z", "JoJo no Kimyou na Bouken: Diamond wa Kudakenai", "Ouran Koukou Host Club", "Mushishi", "Doraemon (1979)")

calculate_culture_score <- function (fav_anime) {
  anime_from_data <- filter(animes, name == fav_anime)
  if (nrow(anime_from_data) == 0) { # no result
    rating <- MIN_SCORE
  } else {
    rating <- anime_from_data$rating
  }
  culture.score <- (MAX_SCORE - rating)^2
  #if (culture.score < 1) {
    #print("Ah, I see you're a man of culture as well.")
  #}
  return(culture.score)
}

weeb.scores <- sapply(fav_animes, calculate_culture_score)

df <- data.frame(Student = students, Score = weeb.scores, stringsAsFactors = TRUE) # want names as factors for plotting
  
df <- df[order(df$Score), ,]  # sort by ranking
df$Student <- factor(df$Student, levels = df$Student)  # to retain the order in plot

g <- ggplot(df, aes(x=Student, y=Score, text = paste("Anime: ", rownames(df)))) + 
  geom_bar(stat="identity", width=.5, fill="tomato3") + 
  labs(title="Class Rankings", 
       subtitle="Culture Score", 
       caption="source: In-Class Survey") + 
  theme(axis.text.x = element_text(angle=65, vjust=0.6))

ggplotly(g, tooltip = c("text", "x"))
```

# The scale is thrown off by one NA. Let's try again removing the outlier.
```{r}
df <- df[1:nrow(df)-1,] # chop off last row
g <- ggplot(df, aes(x=Student, y=Score, text = paste("Anime: ", rownames(df)))) + 
  geom_bar(stat="identity", width=.5, fill="tomato3") + 
  labs(title="Class Rankings", 
       subtitle="Culture Score", 
       caption="source: In-Class Survey") + 
  theme(axis.text.x = element_text(angle=65, vjust=0.6))

ggplotly(g, tooltip = c("text", "x"))
```

